Finally Tagless, Partially Evaluated

### 2008-09-10 tagless/tagless-final.tex
Don't cite haskell-list

\ifshort\else
However we represent an object term,
the representation can be created either by hand (for example, by
entering object terms at a metalanguage interpreter's prompt) or
by parsing and type-checking text.
It is known how to write such a parser and type-checker,
whether using fancy types \citep{Guillemette-Monier-PLPV,haskell-list,WalidICFP02} or not \citep{baars-typing}.
We have ourselves implemented a parser and type-checker for our object
language, which returns (either a parse or type error or) a finally
encoded object term that can then be interpreted in multiple ways
without repeated type-checking.  We leave this problem aside in the
rest of this paper.
\fi

>>>>

\ifshort\else
However we represent an object term,
the representation can be created either by hand (for example, by
entering object terms at a metalanguage interpreter's prompt) or
by parsing and type-checking text.
It is known how to write such a type checker
for a higher-order object language such as ours,
whether using fancy types \citep{Guillemette-Monier-PLPV,WalidICFP02} or not \citep{baars-typing}.
We have ourselves implemented a type checker for our object
language (in the accompanying source file |IncopeTypecheck.hs|),
which maps an ordinary syntax tree to (either a type error or) a finally
encoded object term that can then be interpreted in multiple ways
without repeated type-checking.  We leave this problem aside in the
rest of this paper.
\fi
